Feshbach resonance in confined geometry

### 2015-05-15 term-paper/paper.tex
[term-paper] conclud

\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Introduction}
In the field of ultra-cold atoms and molecules, the collisional properties between the particles play an important role, e.g. for cooling into quantum degeneracy. The strengh of this interaction, the scattering length, can be tuned in the experiment using Feshbach resonance, which appears as a divergence in the scattering length when the energy of a molecular bound state is tuned to match or closed to the energy of the free atom state. This easy tunability of the interaction between particles opens the door for engineering the interaction and using it as a source of correlation and entanglement in a many-body system. The bound state that appears on one side of the Feshbach resonance have also been used to create ultra-cold molecules from ultra-cold atoms.\\

@@

In this review, we will present a formal way to handle this problem. We will first study the generic $S$-wave scattering problem and derive the generic expression for the scattering length. In the second section, we will apply this method to the lower dimensional problem and use it to derive the energy of bound states with the present of external confinement in a one dimensional system.

@@

\section{Conclusion}

>>>>

\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Introduction}
In the field of ultra-cold atoms and molecules, the collisional properties between the particles play an important role, e.g. for cooling into quantum degeneracy. The strengh of this interaction, the scattering length, can be tuned in the experiment using Feshbach resonance, which appears as a divergence in the scattering length when the energy of a molecular bound state is tuned to match or closed to the energy of the free atom state. This easy tunability of the interaction between particles opens the door for engineering the interaction and using it as a source of correlation and entanglement in a many-body system. The bound state that appears on one side of the Feshbach resonance have also been used to create ultra-cold molecules from ultra-cold atoms.\cite{jila-krb}\\

@@

In this review, we will present a formal way to handle this problem. We will first study the generic $S$-wave scattering problem and derive the generic expression for the scattering length. In the second section, we will apply this method to the lower dimensional problem and use it to derive the energy of bound states with the present of external confinement in a one dimensional system\cite{feshbach-lecture-note}.

@@

\section{Conclusion}
We have shown that the low energy $S$-wave scattering can be described by a single parameter, the scattering length $a$. Due to the strong interaction energy caused by a Feshbach resonance, the interaction can be modified by higher vibrational excitations of the trap. As an example, we have shown that there are additional bound state in the present of the confinement.
